---
title: "How to use GetLattesData"
author: "Marcelo Perlin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use GetLattesData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[Lattes](http://lattes.cnpq.br/) is an unique and largest platform for academic curriculumns. There you can find information about the academic work of **all** Brazilian scholars. It includes institution of PhD, current employer, field of work, all publications metadata and more. It is an unique and reliable source of information for bibliometric studies. 

I've been working with Lattes data for some time. Here I present a short list of papers that have used this data.

-  [The Brazilian scientific output published in journals: A study based on a large CV database](http://www.sciencedirect.com/science/article/pii/S1751157716301559)

- [The researchers, the publications and the journals of Finance in Brazil: An analysis based on resumes from the Lattes platform](http://bibliotecadigital.fgv.br/ojs/index.php/rbfin/article/view/47157)    

- [Análise do Perfil dos Acadêmicos e de suas Publicações Científicas em Administração (in Portuguese)](http://www.scielo.br/scielo.php?script=sci_arttext&pid=S1415-65552017000100062)

- Predatory publications in the Brazilian academic system: an empirical analysis (Working paper)

Package `GetLattesData` is a wrap up of the functions that I've been using for acessing the dataset. It's main innovation is the possibility of downloading data directly from Lattes, without any manual work or captcha solving. 


# Example of usage

Let's consider a simple example of downloading information for a group of scholars. I selected a couple of coleagues at my university. Their Lattes id can be easilly found in [Lattes website](http://lattes.cnpq.br/). After searching for a name, notice the internet address of the resulting CV, such as [http://buscatextual.cnpq.br/buscatextual/visualizacv.do?id=K4713546D3](http://buscatextual.cnpq.br/buscatextual/visualizacv.do?id=K4713546D3). Lattes ID is the final 10 digit code of this address. In our case, it is  `'K4713546D3'`.

Since we all work in the business department of UFRGS, the impact of our publications is localy set by the Qualis ranking of Management, Accounting and Tourism (`'ADMINISTRAÇÃO PÚBLICA E DE EMPRESAS, CIÊNCIAS CONTÁBEIS E TURISMO'`). Qualis is the local journal ranking in Brazil. You can read more about Qualis in [Wikipedia](https://en.wikipedia.org/wiki/Qualis_(CAPES)) and [here](http://www.sciencedirect.com/science/article/pii/S1751157716301559)

Now, based on the two sets of information, vector of ids and field of Qualis, we can use `GetLattesData` to download all up to date information about the researchers:

```{r}
library(GetLattesData)

# ids from EA-UFRGS
my.ids <- c('K4713546D3', 'K4440252H7', 
            'K4783858A0', 'K4723925J2')

# qualis for the field of management
field.qualis = 'ADMINISTRAÇÃO PÚBLICA E DE EMPRESAS, CIÊNCIAS CONTÁBEIS E TURISMO'

l.out <- gld_get_lattes_data(id.vec = my.ids, field.qualis = field.qualis)
```

The output `my.l` is a list with three items:

```{r}
names(l.out)
```

The first is a dataframe with information about researchers:

```{r}
tpesq <- l.out$tpesq
str(tpesq)
```

The second dataframe contains information about all publications, including Qualis and SJR:

```{r}
tpublic <- l.out$tpublic
str(tpublic)
```

The third element of the list provides information about all academic supervisions of each researcher:

```{r}
tsupervisions <- l.out$tsupervisions
str(tsupervisions)
```

## An application of  `GetLattesData`

Based on `GetLattesData` and other packages, it is easy to create academic reports for a large number of researchers. See next, where we plot the number of publications for each researcher, conditioning on Qualis ranking.

```{r}
library(ggplot2)

p <- ggplot(tpublic, aes(x = qualis)) +
  geom_bar(position = 'identity') + facet_wrap(~name) +
  labs(x = paste0('Qualis: ', field.qualis))
print(p)
```

We can also use `dplyr` to do some simple assessment of academic productivity:

```{r}
library(dplyr)

my.tab <- tpublic %>%
  group_by(name) %>%
  summarise(n.papers = n(),
            max.SJR = max(SJR, na.rm = T),
            mean.SJR = mean(SJR, na.rm = T),
            n.A1.qualis = sum(qualis == 'A1', na.rm = T),
            n.A2.qualis = sum(qualis == 'A2', na.rm = T),
            median.authorship = median(as.numeric(order.aut), na.rm = T ))

knitr::kable(my.tab)
```
