---
title: "How to use GetLattesData"
author: "Marcelo Perlin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use GetLattesData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

[Lattes](http://lattes.cnpq.br/) in the largest and unique platform for academic curriculumns. In there you can find information about the academic work of **ALL** Brazilian scholars. It is an unique and reliable source of information for bibliometric studies. 

I've been working with Lattes data for some time. Here I present a short list of papers that have used this data.

-  [The Brazilian scientific output published in journals: A study based on a large CV database](http://www.sciencedirect.com/science/article/pii/S1751157716301559)
- Predatory publications in the Brazilian academic system: an empirical analysis (Working paper)
- [The researchers, the publications and the journals of Finance in Brazil: An analysis based on resumes from the Lattes platform](http://bibliotecadigital.fgv.br/ojs/index.php/rbfin/article/view/47157)    
- [Análise do Perfil dos Acadêmicos e de suas Publicações Científicas em Administração (in Portuguese)](http://www.scielo.br/scielo.php?script=sci_arttext&pid=S1415-65552017000100062)

Package `GetLattesData` is a wrap up of the functions that I've been using for acessing this dataset. It's main innovation is the possibility of downloading data directly from Lattes, without any kind of manual work. 

# Example of usage

Let's consider a simple example of downloading information for a group of scholars. I selected a couple of coleagues at my university. Their Lattes id can be easilly found in [Lattes website](http://lattes.cnpq.br/). After searching for a name, notice the internet address of the resulting CV, such as [http://buscatextual.cnpq.br/buscatextual/visualizacv.do?id=K4713546D3](http://buscatextual.cnpq.br/buscatextual/visualizacv.do?id=K4713546D3). Lattes ID is the final 10 digit code of this address. In our case, it is  `'K4713546D3'`.

Since we all work in the business department of the university, the quality of our publications is set by the Qualis rankings of field  `'ADMINISTRAÇÃO PÚBLICA E DE EMPRESAS, CIÊNCIAS CONTÁBEIS E TURISMO'`. Qualis is the local journal ranking in Brazil. You can read more about Qualis in [Wikipedia](https://en.wikipedia.org/wiki/Qualis_(CAPES)) and [here](http://www.sciencedirect.com/science/article/pii/S1751157716301559)

Now, based on the two sets of information, vector of ids and field of Qualis, we can use `GetLattesData` to download all up to date information about the researchers:

```{r}
library(GetLattesData)

# ids from EA-UFRGS
my.ids <- c('K4713546D3',  'K4123414D0', 'K4765099U6', 'K4440252H7', 'K4783858A0',
            'K4769290Y6', 'K4723925J2', 'K4763474Y5')

# qualis for the field of management
field.qualis = 'ADMINISTRAÇÃO PÚBLICA E DE EMPRESAS, CIÊNCIAS CONTÁBEIS E TURISMO'

l.out <- gld_get_lattes_data(id.vec = my.ids, field.qualis = field.qualis)
```

The output `my.l` is a list with two items:

```{r}
names(l.out)
```

The first is a dataframe with information about researchers:

```{r}
tpesq <- l.out$tpesq
str(tpesq)
```

and the second dataframe containing information about all publications, including Qualis and SJR:

```{r}
tpublic <- l.out$tpublic
str(tpublic)
```

## An application of  `GetLattesData`

Based on `GetLattesData` and other packages, it is easy to create academic reports such as the one provided next, where we plot the number of publication for each researcher, conditioning on Qualis ranking.

```{r}
library(ggplot2)

p <- ggplot(tpublic, aes(x = qualis)) +
  geom_bar(position = 'identity') + facet_wrap(~name) +
  labs(x = paste0('Qualis: ', field.qualis))
print(p)
```

